### 2019-02-14 2-Chapters/4-Chapter/IEEE_WCNC__2019__Paper__BMBM.git/IEEE_WCNC__2019__Paper__BMBM.tex
Okay for bibtex

\paragraph{Future works}
%
The utility and impact of the proposed approaches for LPWA networks motivates us to address several subjects as future works. Among them, the non-stationarity of the channel occupancy caused by the learning policy employed by the IoT devices.
%
For that end, modifications of MAB algorithms have been proposed, such as Sliding-Window-\UCB{} or Discounted-\UCB{} \cite{Garivier08}
or more recently M-\UCB{} \cite{CaoZhenKvetonXie18},
% or more recently GLR-\UCB{} \cite{Besson2019GLRT},
that nevertheless have not been explored for the targeted problem.
Chapter~\ref{chapter:6} is focusing on this direction, but we did not have enough time to explore the possible applications of MAB policies designed for non-stationary problems to the model with retransmissions presented in this section.

>>>>

\paragraph{Future works}
%
The utility and impact of the proposed approaches for LPWA networks motivates us to address several subjects as future works. Among them, the non-stationarity of the channel occupancy caused by the learning policy employed by the IoT devices.
%
For that end, modifications of MAB algorithms have been proposed, such as Sliding-Window-\UCB{} or Discounted-\UCB{} \cite{Garivier11UCBDiscount}
or more recently M-\UCB{} \cite{CaoZhenKvetonXie18},
% or more recently GLR-\UCB{} \cite{Besson2019GLRT},
that nevertheless have not been explored for the targeted problem.
Chapter~\ref{chapter:6} is focusing on this direction, but we did not have enough time to explore the possible applications of MAB policies designed for non-stationary problems to the model with retransmissions presented in this section.
